CTest Integration of Sikuli Automated GUI Testing

### 2011-06-21 Documentation/Article.tex

Sikuli's integration with CTest has provided us with numerous advantages in the
measure of productivity and convenience. But our goals are still
hindered by a few limitations.
%\subsection{Text Recognition}
%Sikuli's newer versions come equipped with a text recognition feature whereby
%one can search for a string of text instead of searching for the image of the
%text in the GUI.  This makes programming in Sikuli much simpler but it is
%limited by it's searchable text fonts.
\subsection{Off-screen Rendering}
Our goal in using CTest is that we will be able to test our software
automatically every night and bugs can be reported the next day on CDash.  But
Sikuli is not easily compatible with off-screen rendering.  Sikuli requires
that the screen remains on so that the script can identify the images on the
screen.  In addition, external mouse and keyboard actions can disrupt the script
at any moment.  These factors make it more difficult to set up automated
nightly tests.  
\subsection{Variation of style between machines}
%Different OS, different look => failures
%Even on the same OS, GUI can look different = > failures
Another important issue is the difference between operating systems. 
Developers need to make sure that their software runs on each
OS.  But Different operating systems require different libraries for
generating GUI images. Therefore fonts, icons, and even
layouts will differ between machines. This is also true between versions of the
same OS. So, GUI tests that pass on one machine will inevitably fail on another
machine for the same exact software. This requires developers to write the
same Sikuli script using images from each OS, which will be many times the
workload.

>>>>

Sikuli's integration with CTest has provided us with numerous advantages in the
measure of productivity and convenience. But our goals are still
hindered by a few limitations.

%\subsection{Text Recognition}
%Sikuli's newer versions come equipped with a text recognition feature whereby
%one can search for a string of text instead of searching for the image of the
%text in the GUI.  This makes programming in Sikuli much simpler but it is
%limited by it's searchable text fonts.

\subsection{Off-screen Rendering}

Our goal in using CTest is that we will be able to test our software 
automatically every night and bugs can be reported the next day on CDash. 
But Sikuli is not easily compatible with off-screen rendering. Sikuli 
requires that the screen remains on so that the script can identify the 
images on the screen. In addition, external mouse and keyboard actions can 
disrupt the script at any moment. These factors make it more difficult to 
set up automated nightly tests.

\subsection{Variation of style between machines}

Another important issue is the difference between operating systems.
Developers need to make sure that their software runs on each OS. But
Different operating systems require different libraries for generating GUI
images. Therefore fonts, icons, and even layouts will differ between
machines. This is also true between versions of the same OS. So, GUI tests
that pass on one machine will inevitably fail on another machine for the
same exact software. This requires developers to write the same Sikuli 
script using images from each OS, which will be many times the workload.
